---
output:
  BiocStyle::html_document
toc: true
filters:
  - webr
engine: knitr
webr:
  repos:
    - https://bioc.r-universe.dev
    - https://repo.r-wasm.org
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
#| include: FALSE
library(BiocStyle)
```

# Introduction

In this module, we will be working with the infrastructure R packages available via the [Bioconductor](https://bioconductor.org/) to work with .fcs files in R. We will compare the similarities and differences between the `r Biocpkg("flowCore")` and `r Biocpkg("flowWorkspace")`. As with the other modules, we will be taking advantage of WebR's functionalities to demonstrate some of the functionalities within the browser. Please download the materials for this module for more computational intensive components.  


# Basic concepts

```{webr-r}
webr::install("flowWorkspace")
```

```{r}
?flowWorkspace::gh_pop_get_data()
```

```{webr-r}
?flowWorkspace::gh_pop_get_data()
```
